An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-04-23 poly-embed-journal/poly-embed-journal.tex
Ironing out statements in section 5

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
	Let $\R$ be a finite representative set for $L$ eliciting $\Gamma$.
	The following are equivalent:
	\begin{enumerate}
		\item[a.] $\R$ is a minimum representative set for $L$.
		\item[b.] $L|_\R$ is non-redundant.
		\item[c.] For all $r \in \R$, $\Gamma_r$ is full-dimensional, the multiset $\{\Gamma_r : r \in \R\}$ has no duplicate elements, and $\cup_{r\in\R} \Gamma_r = \simplex$.
	\end{enumerate}
\end{proposition}
\begin{proof}[Sketch]
	$(a \implies b)$  
	We show the contrapositive: suppose $L|_\R$ is redundant.
	Then there is a $r,r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
	Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
	Therefore, $\R \setminus \{r\}$ still a representative set, so $\R$ is not minimum.

@@

\begin{corollary}
	If $\R$ is a minimum representative set for $L$ eliciting $\Gamma$, then $L$ tightly embeds $L|_\R$.
\end{corollary}

@@

\begin{corollary}
	$\trim(L)$ is unique.
\end{corollary}
This follows from Proposition~\ref{prop:tfae-min-rep-nonredundant}, as $\trim(L)$ moves from $L$ to remove any non-redundant reports.
$\trim$ removes redundancy of strict subsets (that is, $\Gamma_r \subseteq \Gamma_{r'}$) by the set comprehension, while it removes fully redundant losses ($\Gamma_r = \Gamma_{r'}$) by definition of a set.

>>>>

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
	Let $\R$ be a finite representative set for $L$ eliciting $\Gamma$.
	The following are equivalent:
	\begin{enumerate}
		\item[a.] $\R$ is a minimum representative set for $L$.
		\item[b.] $L|_\R$ is non-redundant.
		\item[c.] $\Gamma_r$ is full-dimensional for all $r \in \R$, the multiset $\{\Gamma_r : r \in \R\}$ has no duplicate elements, and $\cup_{r\in\R} \Gamma_r = \simplex$.
	\end{enumerate}
\end{proposition}
\begin{proof}[Sketch]
	$(a \implies b)$  
	We show the contrapositive: suppose $L|_\R$ is redundant.
	Then there is a $r,r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
	Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
	Therefore, $\R \setminus \{r\}$ still a representative set, so $\R$ is not minimum.

@@

\begin{corollary}
	If $\R$ is a minimum representative set for $L$, then $L$ tightly embeds $L|_\R$.
\end{corollary}
\jessie{I think we want a little bit more than this, as we want flexibility for bijections of the reports.  Testing}
\begin{corollary}
	If $\R$ is a (finite) minimum representative set for $\ell$ and $L$ embeds $\ell$, then $L$ tightly embeds $\ell$.
\end{corollary}

@@

\begin{corollary}
	For the loss $L: \R \to \reals^\Y_+$, $\trim(L)$ is unique.
\end{corollary}
This follows from Proposition~\ref{prop:tfae-min-rep-nonredundant}, as $\trim(L)$ moves from $L$ to remove any non-redundant reports.
$\trim$ removes redundancy of strict subsets (that is, $\Gamma_r \subseteq \Gamma_{r'}$) by the set comprehension, while it removes fully redundant losses ($\Gamma_r = \Gamma_{r'}$) by definition of a set.
